BIOL 274 Homework 7

### 2024-03-29 bio_dynamics/bio274_filing_cabinet.Rmd
biohw

>>>>

```{r}
# Define the rate equation:
lynx_hare_eq <- c(
  dHdt ~ r * H - b * H * L,
  dLdt ~ e * b * H * L - d * L
)

# Define the parameters (as a named vector):
lynx_hare_params <- c(r = 2, b = 0.5, e = 0.1, d = 1)

# Define the initial condition (as a named vector):
lynx_hare_init <- c(H = 1, L = 3)

# Define deltaT and the number of time steps:
deltaT <- 0.05
n_steps <- 200

# Compute the solution via Euler's method:
out_solution <- euler(system_eq = lynx_hare_eq,
                      parameters = lynx_hare_params,
                      initial_condition = lynx_hare_init,
                      deltaT = deltaT,
                      n_steps = n_steps
                      )

# Make a plot of the solution,
# using different colors for lynx or hares:
ggplot(data = out_solution) +
  geom_line(aes(x = t, y = H), color = "red") +
  geom_line(aes(x = t, y = L), color = "blue",linetype='dashed') +
  labs(
    x = "Time",
    y = "Lynx (red) or Hares (blue/dashed)"
  )
```

```{r}
ggplot(data = out_solution) +
  geom_path(aes(x = L, y = H)) +
  labs(
    x = "Lynx",
    y = "Hares"
  )
```

```{r}

lin_eq <- c(
  dxdt ~ a * x + b * y,
  dydt ~ c * x + d * y
)

# Define the parameters (as a named vector):
lin_params <- c(a = 1, b = 2, c = 3, d = 2)

# Define the initial condition (as a named vector):
lin_init <- c(x = -0.5, y = 0.5)

# Define deltaT and the number of time steps:
deltaT <- 0.01
n_steps <- 200

# Compute the solution via Euler's method:
out_solution <- euler(system_eq = lin_eq,
                      parameters = lin_params,
                      initial_condition = lin_init,
                      deltaT = deltaT,
                      n_steps = n_steps
                      )

ggplot(data = out_solution) +
  geom_line(aes(x = x, y = y))+
  xlim(-5,5)+
  ylim(-5,5)
```

### 2024-03-29 bio_dynamics/bio274_hw7.Rmd
biohw

---
title: "BIOL 274 Homework 7"
author: "Ruby Krasnow"
date: "2024-03-24"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---
# Visualizing Solutions of Linear Systems with Constant Coefficients

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

>>>>

---
title: "BIOL 274 Homework 7"
author: "Ruby Krasnow"
date: "2024-03-28"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---
# Visualizing Solutions of Linear Systems with Constant Coefficients

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(phaseR)
library(ggplotify)
library(demodelr)
```

@@

## Phase Portraits

```{r}
fun <- function(t, y, parameters) {
  x <- y[1]
  y <- y[2]

  a <- parameters[1]
  b <- parameters[2]
  c <- parameters[3]
  d <- parameters[4]

  dy <- numeric(2)

  dy[1] <- a*x + b*y
  dy[2] <- c*x + d*y

  return(list(dy))
}

```

```{r, echo=FALSE, results='hide'}
fun2 <- c(dx ~ x+2*y, dy ~3*x+2*y)
p1 <- phaseplane(fun2,x_var="x",y_var="y", x_window = c(-7, 7), y_window = c(-7, 7))

y0 <- matrix(c(0, 1, 0, 4, -6, 1, 5, 0.5, 0, -3), 5, 2, byrow = TRUE)

y2 <- tibble(x=c(0,0,-6,5,0), y=c(1,4,1,0.5,-3), IC=c("V1", "V2", "V3", "V4", "V5"))%>% mutate(pt = paste0("(",x, ",", y, ")"))
```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.keep = "none"}
traj <- trajectory(fun, y0 = y0,tlim= c(0, 1), 
                   parameters = c(1, 2, 3, 2), add=FALSE)

t <- c(traj$t)

x <- as_tibble(traj$x) %>% bind_cols("t"=t) %>% 
  pivot_longer(cols = c(1:5), names_to = "IC", values_to = "x")

y <- as_tibble(traj$y) %>% bind_cols("t"=t) %>% 
  pivot_longer(cols = c(1:5), names_to = "IC", values_to = "y")

z <- left_join(x,y) %>% filter(x<7 & x>-7 & y<7 & y>-7) %>% left_join(y2 %>% select(IC, pt), by="IC")

```

```{r}
p1+theme_classic()+
  geom_abline(slope=-1, color="gray", linewidth=1)+
  geom_abline(slope=3/2, color="gray", linewidth=1)+
  geom_path(data=z, aes(x=x, y=y, color=pt), linewidth=1.5)+
  geom_point(data=y2, aes(x=x,y=y, color=pt), shape=21, fill="white",size=5, stroke=2)+labs(color="IC")

```
